---
title: "RMD Python Example"
author: "Hadrien@rstudio.com"
date: "11/20/2019"
output: html_document
---

First, we customize our python session:

```{r python-setup, include=FALSE}

# load reticulate
library(reticulate)
# Q: is reticulate automatically loaded already?

#########################################################################
# OPTIONAL: set up a virtual environment to manage your python packages #
#########################################################################

# check what virtual environments already exist
virtualenv_list()

# by default, your python session will use system python. Here we indicate which virtual environment to use for this project
use_virtualenv("my-virtual-environment")

# install python packages
# virtualenv_install(envname = "my-virtual-environment", packages = "pandas")	

# check which version of python you are using
py_config()

# specify which python version to use
use_python("/usr/bin/python3") # option 1
Sys.setenv(RETICULATE_PYTHON="/opt/python/3.6.7/bin/python3") # option 2




```

In addition to R, RStudio can be used to execute other code such as SQL, Bash, and Python.
```{r r-data}
# load data
df <- mtcars # save to R object
```

Access R objects from python

```{python}
import pandas
my_python_object = r.df[r.df['mpg'] > 20]
print(my_python_object)
```



```{python py-data}
# check object type
type(r.df)
type(my_python_object)

# print r.df
print(r.df)
```

Access python objects from R
```{r}
py$my_python_object
```

Plot in python
```{python python-plot}
import matplotlib as mpl
mpl.scatter(my_python_object.mpg, my_python_object.hp)
mpl.show()

```

## Q&A 

_How can I check with version of Python I am using?_ 
Run the command `reticulate::py_config()`

_How do I interpret the output of py_config?_

_How can I confirm if I have a Python session running in parallel to my R session?_ 

_Do I need to use virtual environments?_ 
No. Although setting up virtual environments is recommended for reproducibility and avoiding breaking changes, reticulate will use the system python installation and packages by default.

_If using system python, how can I install new Python packages not previously installed by the server admin?_

_How do I check which Python packages are installed in my virtual environment_?
Use the command `pip freeze`

_How can I execute Python code line by line from RMD without getting KeyError?_
You should be able to. It's possible there was a problem with your python session which is causing the error. Run `reticulate::py_config()` and review the output.

_How can the sys admin set the default version of Python to the correct version?_